---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# schoolhealth

<!-- badges: start -->
<!-- badges: end -->

The goal of schoolhealth is to provide quick and easy access to version-controlled information pertaining to the student and school surveys, as well as document analytic approaches to using these data. More concretely, the schoolhealth package loads meta-information, such as codebooks and factor variables, that are critical to reproducible research and evaluation. 

If this package proves useful moving forward, additional information will be provided as necessary.

## Installation

You can install the development version of schoolhealth from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("ztimpe/schoolhealth")
```

## Student Survey Codebook

After installation and loading the package, call the codebook like you would any other R function:

```{r example}
library(schoolhealth)
codebook <- student_codebook
head(codebook)
```

## Factor Variables

The student and school surveys are almost exclusively multiple choice questions. When analyzing these data in R, casting these variables as factors has a number of advantages, particularly when displaying tables of statistics because the order of the factor can be preserved and that response options receiving zero endorsements are included in output.

```{r factor_example}
factor_variables <- student_codebook_factors
factor_variables[1]
```

Provide example of factor summary:
```{r cars}
table(student_survey$Q30)
```

Summarize the unweighted data.
```{r}
library(dplyr,warn.conflicts = FALSE)
student_survey |>
   count(Q1)|>
   na.omit()|>
   mutate(
          pct = paste0(round(n/sum(n,na.rm=T),2)*100,'%')
          )
```

We recommend using the srvyr package for analyses with weighted data. 

```{r, eval = TRUE}
library(srvyr,warn.conflicts = FALSE)
 student_survey |>
    select(ncessch:race)|>
    as_survey_design(
       ids = ncessch,
       weights = finalwt,
       fpc = district_schools
    )|>
    group_by(Q1)|>
    summarise(mean = round(survey_mean(),2))
```

